ManuscriptPURFits

### 2024-02-23 Code/ManuscriptPURFits.Rmd
Added table of pvalues Ask how to import to manuscript

>>>>

```{r WLAnovaTable, include = FALSE}

WLAnovaTable <- ANOVA_AllWL %>% 
  filter(WL2 == "Red") %>% 
  mutate(Strain = factor(Strain, levels = c("MED4", "SS120", "MIT9313")),
         O2_uM = factor(O2_uM, levels = c(250, 25, 2.5))) %>% 
  select(-c(p.value)) %>% 
  arrange(Strain, O2_uM)

```{r WLAnovaTable, fig.height = 6, fig.width = 8, echo = FALSE }

knitr::kable(WLAnovaTable,
             caption = "pvalues for each ANOVA comparison of fit of red and blue light in each O~2~ experiment for each strain.",
            col.names =  c("Strain",
                           "[O~2~] (µM)",
                          "WL1",
                          "WL2",
                          "pvalue"),
              align = "lcccc"
             )
```
